Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-15 ieee_paper.tex
Added combined swizzling_lane figure.
sply plots

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/swizzling.pdf}
  \includegraphics[width=\linewidth]{figures/channel_permutation.pdf}

  \caption{Swizzling enables to reorder or broadcast elements within
    each 128 bit group. Permutation enables to reorder or broadcast
    whole 128 bit groups.}
  \label{fig:swizzling_permutation}
\end{figure}

@@

\input{additional_figures}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/swizzling_lanes.pdf}
  \caption{Swizzling enables to reorder or broadcast elements within
    each 128 bit group. Permutation enables to reorder or broadcast
    whole 128 bit groups.}
  \label{fig:swizzling_permutation}
\end{figure}

@@

\def\ww{.13\textwidth}
\begin{figure*}
  \begin{center}
    \subfigure[Supercompact.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/supercompact_matrix-crop.pdf}}%
    \subfigure[Compact.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/compact_matrix-crop.pdf}}%
    \subfigure[Random.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/random_matrix-crop.pdf}}%
    \subfigure[2D, no RCM.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/kd-tree-2d-norcm-crop.pdf}}%
    \subfigure[2D, RCM.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/kd-tree-2d-rcm-crop.pdf}} 
    \subfigure[3D, RCM.]{%
      \label{fig:random} 
      \includegraphics[width=\ww]{figures/kd-tree-3d-norcm-crop.pdf}}%
    \subfigure[3D, RCM.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/kd-tree-3d-rcm-crop.pdf}}%
  \end{center}

  \caption{Different sparsity distributions. In all cases, there are
    32 nonzeros per line and 300 rows. The last four matrices
    corresponds to derivative stencils in 2D (a-b) and 3D (c-d) RBF-FD
    calculations.}
  \label{fig:spy_plots}
\end{figure*}
